Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-07-31 documentation/paper.tex
Partially documented wall cuts

A certain number of cuts are necessarily applied to all data to ensure meaningful results. Otherwise, significant overfitting on biases in the data is likely. This basic quality cut $QualCut(D)$ consists of the following restrictions:
\begin{itemize}
    \item The run was not collected during engineering or testing ($\texttt{run\_type}\neq99$)
    \item Recording was triggered by the camera ($\texttt{trigger\_main}=0$)
    \item Acoustic Parameter is not erroneously large and negative ($log_{10}(\texttt{acoustic\_bubnum})>-100$)
    \item Recorded more than 25 seconds after reaching target pressure ($\texttt{te}>25$)
    \item The bubble position $\chi$ was successfully calculated ($[X, Y, Z]\neq[-100, -100, -100]$)
\end{itemize}

@@

PICO-60 events which include multiple bubbles are \textit{always} neutron events; alpha particles and WIMP candidates never scatter. Thus, no discriminator is required to handle these events, so they are removed. The bubble multiplicity cut $MultiCut(D)$ consists of the following restrictions:
\begin{itemize}
    \item Either 0 or 1 bubbles are detected based on images from the camera ($\texttt{nbub}<2$)
    \item The number of bubbles approximated using the pressure transducer is close to 1 ($0.7<\texttt{dytranCZ}<1.3$)
\end{itemize}

>>>>

A certain number of cuts are necessarily applied to all data to ensure meaningful results. Otherwise, significant overfitting on biases in the data is likely. This basic quality cut $QualCut(D)$ consists of the following restrictions:

\begin{itemize}
    \item The run was not collected during engineering or testing ($\texttt{run\_type}\neq99$)
    \item Recording was triggered by the camera ($\texttt{trigger\_main}=0$)
    \item Acoustic Parameter is not erroneously large and negative ($log_{10}(\texttt{acoustic\_bubnum})>-100$)
    \item Recorded more than 25 seconds after reaching target pressure ($\texttt{te}>25$)
    \item The bubble position $\chi$ was successfully calculated ($[X, Y, Z]\neq[-100, -100, -100]$)
\end{itemize}

@@

PICO-60 events which include multiple bubbles are \textit{always} neutron events; alpha particles and WIMP candidates never scatter. Thus, no discriminator is required to handle these events, so they are removed. The bubble multiplicity cut $MultiCut(D)$ consists of the following restrictions:

\begin{itemize}
    \item Either 0 or 1 bubbles are detected based on images from the camera ($\texttt{nbub}<2$)
    \item The number of bubbles approximated using the pressure transducer is close to 1 ($0.7<\texttt{dytranCZ}<1.3$)
\end{itemize}

\subsection{Wall Cut}

Events that occur near the walls of the vessel have acoustic properties which are notably different from events nearer the center of the vessel. It can be desirable for a discriminator to handle these events correctly; however, Acoustic Parameter does not, and neither does the neural network used in the previous PICO-60 paper. Thus, removing wall events allowed for a more meaningful direct comparison between a new neural network and existing techniques.

The complete wall cut $WallCut(D)$ is a composition of the fiducial cut $FidWallCut(D)$ (which makes use of the 3D position $\chi$), the pressure cut $PresWallCut(D)$ (which uses data from the pressure transducer), and the acoustic wall cut $AcWallCut(D)$ (which uses the banded Fourier transform $\beta _{8}$).
